---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fromScratchR

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

[fromScratchR](https://github.com/pat-alt/fromScratchR) is the accompanying package of [fromScratch](https://github.com/pat-alt/fromScratch) - a book that collects ideas, notes, exercises and code that students of the MSc in Data Science at Barcelona GSE were exposed and/or came up with during their studies. Both the book and this package are meant for educational purposes and cover a broad range of topics. The package primarily serves the purpose of making it easier for readers of the book to engage with relevant R code. Most if not all functions implemented in this package have already been implemented in established packages. Coding them up *from scratch* is an educational exercise for the authors and hopefully interacting with the code is beneficial to readers.  

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("pat-alt/fromScratchR")
```

## Example

Below is a simple example of a function from the book. `rorthogonal` generates a random orthogonal matrix through singular value decomposition. 

```{r example}
library(fromScratchR)
## basic example code
X <- rorthogonal(n=100,5)
crossprod(X)
```


